---
output: github_document
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)

```

# Advanced Research Methods foR Psychologists

This Github repo contains all lesson files used in the *Advanced Research Methods foR Psychologists - Practical Applications in R*, taught at Ben-Gurion University on the Negev (2019-2020). These lessons cover the basics of R, basic frequentist and Bayesian testing, and the basics of linear regression modeling (moderation, prediction, model comparison, etc...).

**Notes:**  

- Please note that some code does not work *on purpose*, to force students to learn to debug. <sub>(Other code might not work because... I'm only human, okay??)</sub>  
- Solutions to exercises are not provided here (yet?). Sorry.

## List of packages

Here is a list of packages used in the course, by lesson:

```{r}
pkgs <- c(
  # 02 data.frames
  "tidyverse", # "reader", "dplyr", "tidyr",
  # 03 misc1
  "Hmisc", "mice", "dplyr", "tidyr", 
  # 04 describing data
  "dplyr", "psych", "ggplot2",
  # 05 testing
  "psych", "apa", "ppcor", "BayesFactor", 
  # 06 regression
  "dplyr", "parameters", "performance", "psych", "see",
  # 07 hierarchical (and dummy)
  "dplyr", "emmeans", "car", "performance",
  # 08 moderation
  "dplyr", "emmeans", "interactions",
  # 09 mediation & curvilinear,
  "ggplot2", "performance", "emmeans", "JSmediation",
  # 10 beyond NHST
   "BayesFactor", "bayestestR", "see",
  # 11 misc2
  "performance", "dplyr", "ggplot2", "GGally", "ggResidpanel"
)
```

You can install all the packages used by running:

```{r echo=FALSE, comment = ""}
pkgs <- sort(unique(pkgs))

cat("pkgs <-",capture.output(dput(pkgs)), fill = 80)
```

```{r eval=FALSE}
install.packages(pkgs, dependencies = TRUE)
```

### To Do

- [ ] Equivalence testing(?)
- [ ] Logistic Regression
