---
output: github_document
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
`%>%` <- dplyr::`%>%`

```

# Advanced Research Methods foR Psychologists

This Github repo contains all lesson files used in the graduate-level course: *Advanced Research Methods foR Psychologists - Practical Applications in R*, taught at Ben-Gurion University on the Negev (fall 2019 semester).

The goal is to impart students with the basic tools to process data, describe data (w/ summary statistics and plots), and finally build, evaluate and compare statistical models (using both the frequentist and Bayesian approach), focusing mostly on linear regression modeling. This course will lay the foundation for the topic-focused courses:

- Structural equation modelling (*SEM*)
- Analysis of factorial designs (*ANOVA*).
- Hierarchical linear models (*HLM*).
- Machine Learning (*ML*).

**Notes:**  

- This repo contains only materials relating to *Practical Applications in R*, and does not contain any theoretical or introductory materials.  
- Please note that some code does not work *on purpose*, to force students to learn to debug. <sub>(Other code might not work because... I'm only human, okay??)</sub>  
- Solutions to exercises are not provided here (yet?). Sorry.

## Setup

You will need:

1. A fresh installation of [**`R`**](https://cran.r-project.org/) (preferably version 3.6 or above).
2. [RStudio](https://www.rstudio.com/products/rstudio/download/) (optional - but I recommend using an IDE).
3. The following packages, listed by lesson:

```{r}
pkgs <- c(
  # 02 data.frames
  "tidyverse", "haven", # "reader", "dplyr", "tidyr",
  # 03 outliers & missing data
  "finalfit", "Hmisc", "mice", "dplyr", 
  # 04 describing data
  "dplyr", "parameters", "summarytools", "psych", "ggplot2",
  # 05 testing
  "psych", "effectsize", "ppcor", "BayesFactor", 
  # 06 regression
  "dplyr", "parameters", "effectsize", "performance", "psychTools", "see",
  # 07 dummy and hierarchical
  "dplyr", "emmeans", "car", "performance",
  # 08 moderation
  "dplyr", "emmeans", "interactions",
  # 09 mediation & curvilinear,
  "ggplot2", "performance", "JSmediation",
  # 10 beyond NHST
   "BayesFactor", "bayestestR", "see",
  # 11 assumption checks & non-parameteric inference
  "performance", "dplyr", "ggplot2", "GGally", "ggResidpanel", "parameters", "permuco"
)
```

<!-- And their versions: -->
```{r, echo=FALSE}
#packinfo <- installed.packages(fields = c("Package", "Version"))
#packinfo[packinfo[,"Package"] %in% pkgs,"Version"]
```

You can install all the packages used by running:

```{r echo=FALSE, comment = "", warning=FALSE}
pkgs <- pkgs %>% unique() %>% sort()

cat("# in alphabetical order:")

pkgs %>% {
  capture.output(dput(.))
} %>% {
  capture.output(cat("pkgs <-", ., fill = 80))
} %>%
  styler::style_text()

```

```{r eval=FALSE}
install.packages(pkgs, dependencies = TRUE)
```

## To Do

- [ ] Logistic Regression (?)
- [ ] Power analysis with `pwr` (?)
